Interval Probability for Fuzzy Quantum Theories

### 2016-07-28 prob.tex
prob.tex \subsection{Interval-valued probability measures} Add citation

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\ffzd}[1]{{\mathbb{F}^{d\;*}_{#1}}}
\def\C{{\mathbb{C}}}
\newcommand{\ff}[1]{\mathbb{F}_{#1}}
\newcommand{\melement}[2]{ \langle #1 | #2 | #1 \rangle}
\newcommand{\expect}[2]{ \langle #1 | #2 | #1 \rangle}
\newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
\newcommand{\gerardo}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{OliveGreen}{Gerardo says: #1}\end{minipage}}}
\newcommand{\andy}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{blue}{Andy says: #1}\end{minipage}}}
\usepackage{tensor}
\newcommand{\rme}{\mathrm{e}}
\newcommand{\rmi}{\mathrm{i}}

@@

\begin{definition}[Core of Interval-valued Probability Measure~\cite{GilboaSchmeidler1994,Marinacci1999,Teran2014}]\label{def:CoreInterval-valuedProbability}
A \emph{core} of an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
is the set 
\[
\mathrm{core}\left(\bar{\mu}\right)=\left\{ \pmeas:\events\rightarrow[0,1]\textrm{ probability measure}\middle|\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\forall E\in\events\right\} \textrm{ .}
\]
\qed\end{definition}

@@

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\ffzd}[1]{{\mathbb{F}^{d\;*}_{#1}}}
\def\C{{\mathbb{C}}}
\newcommand{\ff}[1]{\mathbb{F}_{#1}}
\newcommand{\melement}[2]{ \langle #1 | #2 | #1 \rangle}
\newcommand{\expect}[2]{ \langle #1 | #2 | #1 \rangle}
\newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
\newcommand{\gerardo}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{OliveGreen}{Gerardo says: #1}\end{minipage}}}
\newcommand{\andy}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{blue}{Andy says: #1}\end{minipage}}}
\usepackage{tensor}
\newcommand{\rme}{\mathrm{e}}
\newcommand{\rmi}{\mathrm{i}}
\usepackage{verbatim}

@@

\begin{definition}[Core of Interval-valued Probability Measure~\cite{GilboaSchmeidler1994,Marinacci1999,Teran2014}]\label{def:CoreInterval-valuedProbability}
A \emph{core}\footnote{The core is also called a structure~\cite{Weichselberger2000}.}
of an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
is the set
\[
\mathrm{core}\left(\bar{\mu}\right)=\left\{ \pmeas:\events\rightarrow[0,1]\textrm{ probability measure}\middle|\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\forall E\in\events\right\} \textrm{ .}
\]
\qed\end{definition}

@@

\begin{comment}
\bibliographystyle{plain}
\bibliography{discreteGBKS}
\end{comment}
